Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-06-26 paper/submitted/round2_png/abstract_v4.tex
notation edits

An inverse problem seeks to infer unknown model parameters using observed data. We consider a \textit{goal-oriented inverse problem}, where the goal of inferring parameters is to use them in predicting a quantity of interest (QoI). Recognizing that multiple models of varying fidelity and computational cost may be available to describe the physical system, we formulate a goal-oriented model adaptivity approach that leverages multiple models while controlling the error in the QoI prediction. In particular, we adaptively form a mixed-fidelity model by using models of different levels of fidelity in different subregions of the domain. Taking the solution of the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive an adjoint-based third-order estimate for the QoI error from using a lower-fidelity model. Localization of this error then guides the formation of mixed-fidelity models. We demonstrate the method for example problems described by convection-diffusion-reaction models. For these examples, our mixed-fidelity models use the high-fidelity model over only a small portion of the domain, but result in QoI estimates with small relative errors. We also demonstrate that the mixed-fidelity inverse problems can be cheaper to solve and less sensitive to the initial guess than the high-fidelity inverse problems.

%from karen about v1:
%"minimizing the use of high-fidelity constraints" -> won't make sense
%needs to be expanded + 1-2 sentences on approach; sentence on results needs to be more specific

>>>>

An inverse problem seeks to infer unknown model parameters using observed data. We consider a \textit{goal-oriented inverse problem}, where the goal of inferring parameters is to use them in predicting a quantity of interest (QoI). Recognizing that multiple models of varying fidelity and computational cost may be available to describe the physical system, we formulate a goal-oriented model adaptivity approach that leverages multiple models while controlling the error in the QoI prediction. In particular, we adaptively form a mixed-fidelity model by using models of different levels of fidelity in different subregions of the domain. Taking the solution of the inverse problem with the highest-fidelity model as our reference QoI prediction, we extend previous results to obtain a third-order estimate, evaluated using an adjoint approach, for the QoI error from using a lower-fidelity model. Localization of this error then guides the formation of mixed-fidelity models. We demonstrate the method for example problems described by convection-diffusion-reaction models. For these examples, our mixed-fidelity models use the high-fidelity model over only a small portion of the domain, but result in QoI estimates with small relative errors. We also demonstrate that the mixed-fidelity inverse problems can be cheaper to solve and less sensitive to the initial guess than the high-fidelity inverse problems.

### 2017-06-26 paper/submitted/round2_png/algorithms_v4_cmame.tex
notation edits

As an example, consider a pair of low- and high-fidelity models described by the convection-diffusion and convection-diffusion-reaction equations
\begin{subequations}
\begin{align}
\textrm{low-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u = q, \\
\textrm{high-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = q,
\end{align}
\end{subequations}
where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogenous Dirichlet boundary conditions. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= q,
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient that's zero in the $\Omega_{LF}$ and equal to $k_r$ in $\Omega_{HF}$; initially, $\Omega_{LF}=\Omega$. Let the QoI be described by $I(q,u)=\int_{\Omega_I\subset\Omega} u \:\textrm{d}\Omega$, where $\Omega_I$ is the QoI region. Let the observations be of the state at some set of locations, so that the data-misfit term is $\frac{1}{2}\int_\Omega \delta_{obs}(u-d)^2\:\textrm{d}\Omega$, where $\delta_{obs}$ is a sum of Dirac delta functions indicating the locations of the observations. Let the regularization term be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla q\|_2^2\:\textrm{d}\Omega$, where $\beta$ is a regularization coefficient. Assuming divergence-free velocity $\vec{V}$, the mixed-fidelity model has augmented Lagrangian
\begin{eqnarray}
\mathcal{M}_{MF}((q,u,z)(p,v,y)) &=& \int_{\Omega_I\subset\Omega} u \:\textrm{d}\Omega \nonumber\\
&+& \int_\Omega p(-\beta\nabla^2q+z) \nonumber\\
&+& v(k_d\nabla^2z+\vec{V}\cdot\nabla z+2k^{MF}_rzu+\delta_{obs}(u-d)) \nonumber\\ 
&+& y(k_d\nabla^2u-\vec{V}\cdot\nabla u+k^{MF}_ru^2+q)\:\textrm{d}\Omega.
\end{eqnarray}
Taking variations with respect to the auxiliary variables $(p,v,y)$ recovers the equations for the primary variables; taking variations with respect to the primary variables gives the equations for the auxiliary variables. Solving for the primary variables and then the auxiliary variables gives the stationary point $\Psi_{MF}$ of $\mathcal{M}_{MF}$. The weighted residual of the high-fidelity primary and auxiliary equations, evaluated at $\Psi_{MF}$, describes a linear functional in the weights (see \Cref{eq:supadjout}). Taking the adjoint of these high-fidelity primary and auxiliary systems, with output described by this linear functional, gives the supplementary adjoint; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately. Having obtained $\Psi_{MF}$ and the supplementary adjoint $\Lambda$, we evaluate the error estimate (see Step \ref{alg-line:MFerrorest} of \Cref{alg:refSeries}), localize it (see \Cref{sec:errLocal}), and use the localization to guide the selection of elements currently in $\Omega_{LF}$ to include in $\Omega_{HF}$ in the next iteration. We return to this example and give results of applying \Cref{alg:refSeries} to this pair of models in \Cref{sec:cdvcdr}.

>>>>

As an example, consider a pair of low- and high-fidelity models described by the convection-diffusion and convection-diffusion-reaction equations
\begin{subequations}
\begin{align}
\textrm{low-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u = q, \label{eq:cdvcdrLF}\\
\textrm{high-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = q, \label{eq:cdvcdrHF}
\end{align}
\end{subequations}
where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogenous Dirichlet boundary conditions. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively; initially, $\Omega_{LF}=\Omega$. The resulting mixed-fidelity models can be described by,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= q,
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient, %that's zero in the $\Omega_{LF}$ and equal to $k_r$ in $\Omega_{HF}$; 
%
\begin{equation}
k^{MF}_r=
\begin{cases}
k_r & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Let the QoI be described by $I(q,u)=\int_{\Omega_I} u \:\textrm{d}\Omega$, where $\Omega_I\subset\Omega$ is the QoI region. Let the observations be of the state at some set of locations, so that the data-misfit term is $\frac{1}{2}\int_\Omega \delta_{obs}(u-d)^2\:\textrm{d}\Omega$, where $\delta_{obs}$ is a sum of Dirac delta functions indicating the locations of the observations. Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}, with $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla q\|_2^2\:\textrm{d}\Omega$, where $\beta$ is a regularization coefficient. Assuming divergence-free velocity $\vec{V}$, the mixed-fidelity model has augmented Lagrangian
\begin{eqnarray}
\mathcal{M}_{MF}((q,u,z)(p,v,y)) &=& \int_{\Omega_I\subset\Omega} u \:\textrm{d}\Omega \nonumber\\
&+& \int_\Omega p(-\beta\nabla^2q+z) \nonumber\\
&+& v(k_d\nabla^2z+\vec{V}\cdot\nabla z+2k^{MF}_rzu+\delta_{obs}(u-d)) \nonumber\\ 
&+& y(k_d\nabla^2u-\vec{V}\cdot\nabla u+k^{MF}_ru^2+q)\:\textrm{d}\Omega.
\end{eqnarray}
Taking variations with respect to the auxiliary variables $(p,v,y)$ recovers the equations for the primary variables; taking variations with respect to the primary variables gives the equations for the auxiliary variables. Solving for the primary variables and then the auxiliary variables gives the stationary point $\Psi_{MF}$ of $\mathcal{M}_{MF}$. The weighted residual of the high-fidelity primary and auxiliary equations, evaluated at $\Psi_{MF}$, describes a linear functional in the weights (see \Cref{eq:supadjout}). Taking the adjoint of these high-fidelity primary and auxiliary systems, with output described by this linear functional, gives the supplementary adjoint; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately. Having obtained $\Psi_{MF}$ and the supplementary adjoint $\Lambda$, we evaluate the error estimate (see Step \ref{alg-line:MFerrorest} of \Cref{alg:refSeries}), localize it (see \Cref{sec:errLocal}), and use the localization to guide the selection of elements currently in $\Omega_{LF}$ to include in $\Omega_{HF}$ in the next iteration. We return to this example and give results of applying \Cref{alg:refSeries} to this pair of models in \Cref{sec:cdvcdr}.

### 2017-06-26 paper/submitted/round2_png/intro_v4_cmame.tex
notation edits

Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining an acceptably low error tolerance for the QoI. In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,Park04,PrudOden99,VendDarm00,Yano12} and for model adaptivity~\cite{BraackErn03,OdenPrudetal06}. These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement. %CITE REVIEWER 4 PAPERS HERE (with braack and oden), SAY THAT ONE COULD USE GOAL-ORIENTED-FWD APPROACHES FOR INVERSE PROBLEMS BY RUNNING WITH FWD THAT IS KKT SYSTEM, BUT SAY THAT HERE TAKE ADVANTAGE OF THE PARTICULAR STRUCTURE ON AN INVERSE PROBLEM?

@@

In this paper, we target model adaptivity in the solution of goal-oriented inverse problems. We present a robust, adaptive framework that identifies the subregions of the domain where high-fidelity representation of physics and parameters is important to achieving a desired accuracy in the QoI. To achieve this, we combine ideas from goal-oriented model adaptivity for forward problems and goal-oriented methods for inverse problems. In particular, our method allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction. Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI. 
%We note that while the approach outlined in~\cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.

@@

\red{STILL NEED TO ADD REFERENCES TO THE TWO POINTED OUT BY REVIEWER 4}

>>>>

Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining an acceptably low error tolerance for the QoI. In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,Park04,PrudOden99,VendDarm00,Yano12} and for more general model adaptivity~\cite{OdenVem00,VemOden01,BraackErn03,OdenPrudetal06}. These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement. Approaches for the goal-oriented forward problem can be applied to the inverse problem by treating the optimality conditions of the inverse problem as a forward model, though one more complex than the original forward model. Methods tailored to the goal-oriented inverse problem, including the one proposed in this work, make use of the particular structure of the inverse problem.

@@

In this paper, we target model adaptivity in the solution of goal-oriented inverse problems. We present a robust, adaptive framework that identifies the subregions of the domain where high-fidelity representation of physics and parameters is important to achieving a desired accuracy in the QoI. To achieve this, we combine ideas from goal-oriented model adaptivity for forward problems and goal-oriented methods for inverse problems. In particular, our method allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction. Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we obtain a third-order estimate, evaluated using an adjoint approach, for the QoI error from using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI. 
%We note that while the approach outlined in~\cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.

@@

### 2017-06-26 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
notation edits

\section{Mathematical Formulation}\label{sec:form}
%
\edit{In this section, we clearly define the low, mixed and high fidelity inverse problems. We also develop theoretical results which extend the work of~\cite{} to multimodel settings, in particular obtaining a computable, rigorous error estimate for QoI targeted generation of mixed fidelity formulations of inverse problems.}

%------------------------------------------------------------------------------%
\subsection{Inverse Problem Formulation}  \label{sec:setup}
%------------------------------------------------------------------------------%
%
We begin by defining a generic goal-oriented inverse problem. Given observations (data) $d\in\R^{n_d}$, we seek to infer parameter(s) $q\in Q$, where $Q$ is a Hilbert space. An observation operator $C:U\to\Reals^{n_d}$ relates the parameter to the observations via state variable(s) $u\in U$, where $u$ satisfies,
\begin{equation}
a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\label{eq:weakForm}
\end{equation}
where $U$ is also a Hilbert space. Equation \Cref{eq:weakForm} is called the state equation. The form $a$, and the functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$). Finally, our objective functional or the QoI, is a scalar functional $I(q,u)$, where $I:Q\times U\to\R$.

The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem. Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters. To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation. The regularized inverse problem can thus be written as a constrained optimization problem,
%
\begin{subequations}
\label{eq:invOpt}
\begin{align}
\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_obj} \\
\textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U. \label{eq:invOpt_cons}
\end{align}
\end{subequations}
%
Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.

In an inverse problem, multiple choices are apparent for the structure of the inferred parameter $q$, the data $d$ and state equation. Together these constitute a model for formulating the inverse problem. For example, the parameter $q$ can be modeled as a single scalar value or an infinite dimensional field variable, the data $d$ can be the entire time series of measurements from a sensor, or simply a smaller subset of those measurements. The state equation can be complex, nonlinear relationship requiring an expensive computation to resolve (for e.g./ the Navier Stokes equations) or a linear, single physics diffusion model (for e.g./ Laplace's equation). All these different modeling choices lead to different versions of the optimization problem that would need to be solved to infer the unknown parameter.

We assume that there exists an ideal model for solving the inverse problem, called the high fidelity model. Giving infinite computational resources, we would use this high fidelity to formulate and solve our inverse problem. Mathematically we differentiate this high fidelity inverse problem with the subscript $HF$,
%
\begin{subequations}
\label{eq:invOpt}
\begin{align}
\min\limits_{q,u} & \quad J(q_{HF},u_{HF})=\frac{1}{2}\|d-C(u_{HF})\|_2^2 + R(q_{HF}), \label{eq:invOpt_obj} \\
\textrm{s.t. }& \quad a(u_{HF},q_{HF})(\phi)=\ell(q_{HF})(\phi),\quad\forall\phi\in U_{HF}. \label{eq:invOpt_cons}
\end{align}
\end{subequations}
%
where $q \in Q_{HF}$. Due to the constraints presented by limited computational resources, one may instead attempt to infer the parameter $q$ using a different, less computationally demanding model, which we call the low fidelity model,
%
\begin{subequations}
\label{eq:invOpt}
\begin{align}
\min\limits_{q,u} & \quad J(q_{LF},u_{LF})=\frac{1}{2}\|d-C(u_{LF})\|_2^2 + R(q_{LF}), \label{eq:invOpt_obj} \\
\textrm{s.t. }& \quad a(u_{LF},q_{LF})(\phi)=\ell(q_{LF})(\phi),\quad\forall\phi\in U_{LF}. \label{eq:invOpt_cons}
\end{align}
\end{subequations}
%
where $q \in Q_{LF}$. If there is compatibility between the low fidelity and high fidelity solution spaces for $q$ and $u$, one may combine the two models to solve the inverse problem. The low fidelity model can be used in part of the computational domain, and the high fidelity in the remainder, and such a model is called a mixed fidelity model, which we distinguish by the subscript $MF$.

In a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI). We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$. The QoI evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values. We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use. In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations. We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
%
%------------------------------------------------------------------------------%
\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse Problem}  \label{sec:deriv}
%------------------------------------------------------------------------------%
%
For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
%
\begin{proposition}
\label{thm:error_estimate}
Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}. Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$. Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$. Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.

@@

The above proposition splits the error in the QoI into three components, a third order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$. Although the linear term is not computable, it can be estimated using an appropriate dual problem. We describe one method of estimating this term below.

>>>>

\section{Mathematical Formulation}\label{sec:form}
%
We first introduce the goal-oriented inverse problem. Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed-fidelity and/or lower-fidelity models.

%------------------------------------------------------------------------------%
\subsection{Inverse Problem Formulation}  \label{sec:setup}
%------------------------------------------------------------------------------%
%
Consider a model for which the Galerkin formulation of the weak form is written as
\begin{equation}
a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\label{eq:weakForm}
\end{equation}
where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces. The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$). Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations. The actual observations (data) are denoted by $d\in\R^{n_d}$.

The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem. In our setting, such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters. To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation. The regularized inverse problem can thus be written as a constrained optimization problem,
%
\begin{subequations}
\label{eq:invOpt}
\begin{align}
\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_obj} \\
\textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U. \label{eq:invOpt_cons}
\end{align}
\end{subequations}
%
Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}. The constraints \Cref{eq:invOpt_cons} are typically models of physical processes or systems. A given physical system can be described to varying degrees of fidelity using different models. This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution is of interest.

We consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI). We denote a scalar QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI. We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use. In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations. We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
%
%------------------------------------------------------------------------------%
\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse Problem}  \label{sec:deriv}
%------------------------------------------------------------------------------%
%
For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
%
\begin{proposition}
\label{thm:error_estimate}
Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}. Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$. Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$. Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.

@@

The above proposition splits the error in the QoI into three components, a third-order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$. Although the linear term is not computable, it can be estimated using an appropriate dual problem. We describe one method of estimating this term below.
